Toward dynamic models of combat or lack thereof in animal mating

### 2016-02-07 ms.tex
tex update: costs and maturationtime added

\subsection{Immature phase}
% TODO update this to reflect what happens in the model
% ie pulling the maturation times from the logistic cdf with location and parameters given

@@

while the time $\tau$ taken for a male to grow from $m(0) \rightarrow m$ is then
\begin{equation} \label{eq:tau}
\tau(m_0, m) = \frac1{a(1-b)}\left(m ^{1-b} - m_0 ^{1-b}\right).
\end{equation}

@@

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/k_history.pdf}
    \caption{a line(ish) plot of the aggression parameter $k$ at max energy}
    \label{fig:k history}

    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/e_0_history.pdf}
    \caption{a line(ish) plot of the aggression parameter $e_0$  k at max energy}
    \label{fig:e_0 history}
\end{figure}

>>>>

\subsection{Immature phase}
% TODO update this to reflect what happens in the model

@@

We Pull the maturation time from the logistic distribution with a  location and width parameters.

@@

We are looking at two \'cost functions':
\begin{enumerate}
    \item A flat percentage of the losers maximum energy or...
    \item $$ E_{costs} = \frac {E_{loser max}} {1 + exp(-(\frac{m_{winner} - m_{loser}}{k} - m_0)}$$ Where the fight cost is a function of the losers mass and the winners mass, and a couple of other parameters.
\end{enumerate}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/k_history.pdf}
    \caption{a line(ish) plot of the aggression parameter $k$ at max energy, the grey bounds are the standard deviation}
    \label{fig:k history}

    \includegraphics[width=10cm,height=10cm,keepaspectratio]{figures/e_0_history.pdf}
    \caption{a line(ish) plot of the aggression parameter $e_0$  k at max energy the grey bounds are the standard deviation}
    \label{fig:e_0 history}
\end{figure}
